Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
a few small edits in 5

\begin{theorem}[Soundness of equational theory]
\begin{equation*}
\forall S, T, n . \quad
S \equiv T \; \Rightarrow \;
\interp{S}_n = \interp{T}_n
\end{equation*}
(See the supplement for the proof)
\end{theorem}

@@

\begin{theorem}[Approximation soundness]
Code consistent with a specification $S$
 is consistent with a more general specification $T$,
\ie{}, for all models $M$ of a piece of code:
\begin{equation*}
S <: T \; \wedge (\consA{M}{\interp{S}_n}) \;
\Rightarrow \; (\consA{M}{\interp{T}_n})
\end{equation*}
where $\consAName$ implements consistency in checking (\cref{subsec:checking}).
(See the supplement for the proof)
\end{theorem}

@@

\begin{figure}[t]
\vspace{-0.8em}
\hspace{-0.5em}
\begin{minipage}{0.16\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\quad \\[0em]
\begin{tikzpicture}[scale=0.8]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
\node at (1.25,1.22) {\textnormal{\footnotesize{0,0}}};
\draw[thick] (1,1) rectangle (1.5,1.5);
\draw[thick] (1.5,1) rectangle (2,1.5);
\draw[thick] (1,0.5) rectangle (1.5,1);
\draw[thick] (0.5,1) rectangle (1,1.5);
\draw[thick] (1,1.5) rectangle (1.5,2);
\end{tikzpicture} \\[0em]
(a)
\end{array}
\end{align*}
\end{minipage} $\rightarrow$ \begin{minipage}{0.43\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.35,0) to [round left paren ] (0.35,2);
\draw[thick] (0.5,1) rectangle (2,1.5);
\draw[thick] (1,0.40) rectangle (1.5,0.90);
\draw[thick] (1,1.60) rectangle (1.5,2.10);
\node at (2.3,1.22) {+};
\draw[thick] (3.8,1) rectangle (4.3,1.5);
\draw[thick] (2.6,1) rectangle (3.1,1.5);
\draw[thick] (3.2,0.5) rectangle (3.7,2);
\draw [black, thin] (4.4,0) to [round right paren ] (4.4,2);
\end{tikzpicture} \\[-0.5em] (b)
\end{array}
\end{align*}
\end{minipage}$\rightarrow$ \begin{minipage}{0.25\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.8,0) to [round left paren ] (0.8,2);
\draw[thick] (1,0.5) rectangle (1.5,2);
\node at (1.8,1.22) {+};
\draw[thick] (2.1,1) rectangle (3.6,1.5);
\draw [black, thin] (3.7,0) to [round right paren ] (3.7,2);
%\node at (2.75,1.22) {\textnormal{\small{0,0}}};
\end{tikzpicture} \\[-0.5em] (c)
\end{array}
\end{align*}
\end{minipage}
\caption{Illustration of grouping spans in
inference}
\label{fig:inference-steps-informal}
\vspace{-0.8em}
\end{figure}

@@

\begin{figure}[t]
%\newcommand{\llower}{\vect{x}^L_i}
%\newcommand{\lupper}{\vect{x}^U_i}
\vspace{-0.7em}
\newcommand{\llower}{l}
\newcommand{\lupper}{u}
{\scalebox{0.97}{
\begin{minipage}{1\linewidth}
\begin{align*}
&\mathsf{toSpec} \; d \; (\llower, \lupper) = \\
&\hspace{-0.4em}\begin{cases}
%% POINT
\exact{\stenReflS{d}} & \llower = 0 \, \wedge \, \lupper = 0\\[0.02em]
%% FWD
\exact{\stenFwdS{\lupper}{d}}  & \llower = 0 \, \wedge \, \lupper > 0 \\[0.02em]
\exact{\stenFwdSR{\lupper}{d}{\irreflS}}\!\!\!\! & \llower = 1 \, \wedge \, \lupper > 0 \\[0.02em]
%% BWD
\exact{\stenBwdS{|\llower|}{d}}  & \llower < 0 \, \wedge \, \lupper = 0 \\[0.02em]
\exact{\stenBwdSR{|\llower|}{d}{\irreflS}}\!\!\!\! & \llower < 0 \, \wedge \, \lupper = -1 \\[0.02em]
%% CEN
\exact{\stenCenS{\lupper}{d}}& \llower < 0 \wedge \lupper > 0 \wedge |\llower| = \lupper \\[0.02em]
\exactR(\stenBwdS{|\llower|}{d} & \llower < 0 \wedge \lupper > 0  \wedge |\llower| \neq \lupper \\
\qquad\qquad \texttt{+} \, \stenFwdS{\lupper}{d}) & \\[0.02em]
% BOUND
\upperB{\stenFwdS{\lupper}{d}} & \llower > 1 \\[0.02em]
\upperB{\stenBwdS{|\llower|}{d}} \quad & \llower < (-1)
 \\[0.02em]
% ABSOLUTE REP
\exact{\epsilon} & \llower = \infty \, \vee \, \lupper = \infty
  \end{cases}
\end{align*}
\end{minipage}
}}
\caption{\textsf{toSpec} constructor of $\mathsf{Approx}(\specDNF)$ values.}
\label{fig:to-spec}
\vspace{-0.8em}
\end{figure}

\begin{definition} The $\mathsf{toSpec}$ constructor is defined
in \Cref{fig:to-spec}, where the lower and upper bounds
determine region constants; $\mathsf{toSpec} \, d \, (l, u)$ is always defined
 if $l$ less than or equal to $u$.

>>>>

\begin{theorem}[Soundness of equational theory]
\begin{equation*}
\forall S, T, n . \quad
S \equiv T \; \Rightarrow \;
\interp{S}_n = \interp{T}_n
\end{equation*}
\end{theorem}

@@

\begin{theorem}[Approximation soundness]
Code consistent with a specification $S$
 is consistent with a more general specification $T$,
\ie{}, for all models $M$ of a piece of code:
\begin{equation*}
S <: T \; \wedge (\consA{M}{\interp{S}_n}) \;
\Rightarrow \; (\consA{M}{\interp{T}_n})
\end{equation*}
where $\consAName$ implements consistency in checking (\cref{subsec:checking}).
\end{theorem}

@@

\begin{figure}[t]
\vspace{-1em}
\hspace{-0.5em}
\begin{minipage}{0.16\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\quad \\[0em]
\begin{tikzpicture}[scale=0.8]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
\node at (1.25,1.22) {\textnormal{\footnotesize{0,0}}};
\draw[thick] (1,1) rectangle (1.5,1.5);
\draw[thick] (1.5,1) rectangle (2,1.5);
\draw[thick] (1,0.5) rectangle (1.5,1);
\draw[thick] (0.5,1) rectangle (1,1.5);
\draw[thick] (1,1.5) rectangle (1.5,2);
\end{tikzpicture} \\[0em]
(a)
\end{array}
\end{align*}
\end{minipage} $\rightarrow$ \begin{minipage}{0.43\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\draw[step=0.5cm,lightgray,very thin] (0.5,0.5) grid (2,2);
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.35,0) to [round left paren ] (0.35,2);
\draw[thick] (0.5,1) rectangle (2,1.5);
\draw[thick] (1,0.40) rectangle (1.5,0.90);
\draw[thick] (1,1.60) rectangle (1.5,2.10);
\node at (2.3,1.22) {+};
\draw[thick] (3.8,1) rectangle (4.3,1.5);
\draw[thick] (2.6,1) rectangle (3.1,1.5);
\draw[thick] (3.2,0.5) rectangle (3.7,2);
\draw [black, thin] (4.4,0) to [round right paren ] (4.4,2);
\end{tikzpicture} \\[-0.5em] (b)
\end{array}
\end{align*}
\end{minipage}$\rightarrow$ \begin{minipage}{0.25\linewidth}
\begin{align*}
\setlength{\arraycolsep}{0em}
\begin{array}{c}
\begin{tikzpicture}[scale=0.72]
%\node at (1.25,1.22) {\textnormal{\small{0,0}}};
\draw [black, thin] (0.8,0) to [round left paren ] (0.8,2);
\draw[thick] (1,0.5) rectangle (1.5,2);
\node at (1.8,1.22) {+};
\draw[thick] (2.1,1) rectangle (3.6,1.5);
\draw [black, thin] (3.7,0) to [round right paren ] (3.7,2);
%\node at (2.75,1.22) {\textnormal{\small{0,0}}};
\end{tikzpicture} \\[-0.5em] (c)
\end{array}
\end{align*}
\end{minipage}
\caption{Illustration of grouping spans in
inference}
\label{fig:inference-steps-informal}
\vspace{-0.8em}
\end{figure}

@@

\begin{figure}[t]
%\newcommand{\llower}{\vect{x}^L_i}
%\newcommand{\lupper}{\vect{x}^U_i}
\vspace{-0.7em}
\newcommand{\llower}{l}
\newcommand{\lupper}{u}
{\scalebox{0.95}{
\begin{minipage}{1\linewidth}
\begin{align*}
&\mathsf{toSpec} \; d \; (\llower, \lupper) = \\
&\hspace{-0.4em}\begin{cases}
%% POINT
\exact{\stenReflS{d}} & \llower = 0 \, \wedge \, \lupper = 0\\[0.02em]
%% FWD
\exact{\stenFwdS{\lupper}{d}}  & \llower = 0 \, \wedge \, \lupper > 0 \\[0.02em]
\exact{\stenFwdSR{\lupper}{d}{\irreflS}}\!\!\!\! & \llower = 1 \, \wedge \, \lupper > 0 \\[0.02em]
%% BWD
\exact{\stenBwdS{|\llower|}{d}}  & \llower < 0 \, \wedge \, \lupper = 0 \\[0.02em]
\exact{\stenBwdSR{|\llower|}{d}{\irreflS}}\!\!\!\! & \llower < 0 \, \wedge \, \lupper = -1 \\[0.02em]
%% CEN
\exact{\stenCenS{\lupper}{d}}& \!\!\!\llower < 0 \wedge \lupper > 0 \wedge |\llower| = \lupper \\[0.02em]
\exactR(\stenBwdS{|\llower|}{d} & \!\!\!\llower < 0 \wedge \lupper > 0  \wedge |\llower| \neq \lupper \\
\qquad\qquad \texttt{+} \, \stenFwdS{\lupper}{d}) & \\[0.02em]
% BOUND
\upperB{\stenFwdS{\lupper}{d}} & \llower > 1 \\[0.02em]
\upperB{\stenBwdS{|\llower|}{d}} \quad & \llower < (-1)
 \\[0.02em]
% ABSOLUTE REP
\exact{\epsilon} & \llower = \infty \, \vee \, \lupper = \infty
  \end{cases}
\end{align*}
\end{minipage}
}}
\caption{\textsf{toSpec} constructor of $\mathsf{Approx}(\specDNF)$ values.}
\label{fig:to-spec}
\vspace{-0.8em}
\end{figure}

\begin{definition} The $\mathsf{toSpec}$ constructor is defined
in \Cref{fig:to-spec}, where the lower and upper bounds
determine region constants; $\mathsf{toSpec} \, d \, (l, u)$ is defined
 if $l$ less than or equal to $u$.
